AbxD01 Analysis

### 2014-11-20 abxD01_analysis.Rmd
updated r markdown files
finished code for fig 3, update fig 1

---
title: "AbxD01 Analysis"
author: "Alyx Schubert"
date: "September 29, 2014"
output: pdf_document
---

@@

### TO DO STILL
- change the "0" to be min o 0.001 instead
- add the 1/2 dashed lines
- also wanted to try to make this table in the other direction: Phyla/OTUs as each graph with different shadings or colors for each treatment... will be good for titration graphs

@@

@@

### TO DO STILL
- I want to change the graph so that the OTUs are their own graphs and the titrations are side by side
-once code is working then put up the other titration data files

>>>>

---
title: "AbxD01 Analysis"
author: "Alyx Schubert"
date: "September 29, 2014"
output: word_document
---

@@

### TO DO STILL
- change the "0" to be min of 0.001 instead of 0.0001 relabund
    - **completed 11/20/14, just make sure future files are changed for other graphs using the "abxD01.barcharts.xOTU.test.r"**
- add the 1/2 dashed lines
    - **completed 11/20/14**
- also wanted to try to make this table in the other direction: Phyla/OTUs as each graph with different shadings or colors for each treatment... will be good for titration graphs

@@

This figure shows correlation values for OTUs with next day *C. difficile* CFU levels calculated across the original set of antibiotic experiments.

@@

### TO DO STILL
- I want to change the graph so that the OTUs are their own graphs and the titrations are side by side
- once code is working then put up the other titration data files
- change min relabund from 0.0001 to 0.001 for cef and strep
    - **11/20/14, changed the vanc titrations min**
